\documentclass{res}

\textwidth=6in % increase textwidth to get smaller right margin

\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\begin{document}

\name{\sc Manuel Ignacio G\'omez Chac\'on}
\address{%
  \textbf{Computer engineering}, Universidad Sim\'on Bol\'{\i}var, Venezuela
  \\ Current location: Munich, Germany
  \\ Date of birth: 1988--01--15
}
\address{%
  +49 (176) 36 53 49 72
  \\ \textsc{targen@gmail.com}
  \\ \url{https://linkedin.com/in/mgomezch}
}

\begin{resume}

  \section{Professional orientation}
    \begin{itemize}
      \item Leading software development teams as a people manager and technical lead
      \item Distributed system architecture and implementation
      \item Web API and application backend architecture and implementation
      \item Database design, architecture and administration
      \item Functional programming, programming language theory and implementation
    \end{itemize}

  \section{Technical ecosystems}
    \begin{itemize}
      \item Proficient: AWS, Haskell, Java, C++, shell scripting (POSIX/Bash), PostgreSQL, Git, Vim
      \item Proficient (but it's been a while): Python, JavaScript, C, MySQL, Django, Docker
      \item Basic: Ruby, Go, InfluxDB, PHP, Swift, Mathematica, InfluxDB, Telegraf, Grafana, MongoDB, Apache, Nginx, HAproxy, OpenSSL
    \end{itemize}
  \section{Natural languages}
    Spanish (native), English (fluent), French (basic), German (basic)

\section{Experience}
  \begin{itemize}[leftmargin=-0.3in]
    \setlength\itemsep{1em}

    \item
      \textsc{Google}
      \\ October 2022--Present (Munich, Germany): \textbf{Engineering Manager}, ChromeOS Commercial
      \\ \small{Managing a software development team with 9 reports, building ChromeOS features for enterprise identity provider integrations.}

    \item September--October 2022: relocating to Munich!

    \item
      \textsc{Amazon Web Services}
      \\ November 2021--August 2022 (Berlin, Germany): \textbf{Software Development Manager (III)}\footnote{Transitioning into management since September 2020.}, AWS Billing
      \\ April 2021--November 2021 (Berlin, Germany): \textbf{Senior Software Development Engineer (III)}, AWS Billing
      \\ August 2018--April 2021 (Berlin, Germany): \textbf{Software Development Engineer (II)}, AWS Billing
      \\ \small{Distributed system development and operations in AWS Billing.  Building a front-end application for self-service configuration of products and pricing for all AWS services, with customers across 300+ internal Product Management teams, and high-stakes operations in support of launches for new AWS products, services and regions, and high-visibility events like AWS re:Invent.  Building systems to automate the billing configuration of private deals for enterprise-class AWS customers accounting for 50\% of AWS revenue.  Operational support and incident response.  Application development primarily using Java, supported by extensive use of AWS DynamoDB, S3, SQS, SNS, Lambda, Simple Workflow Service, Step Functions, and Kinesis.}
      \\ \small{Managing two independent software development teams with 15 total reports including one manager and indirect software development engineers, planning roadmaps and investment priorities, growing employee careers through 3 successful promotions, and over 250 completed interviews for 25 successful hires in own and adjacent teams.}

    \item
      \textsc{Zalando SE}
      \\ August 2017--July 2018 (Berlin, Germany): \textbf{Senior Database Engineer}, Platform Infrastructure
      \\ \small{Development of tools and developer-facing UIs for database administration automation and monitoring for hundreds of containerized PostgreSQL high-availability clusters on AWS and Kubernetes using Go, Python, and modern JavaScript, including a Kubernetes operator for a PostgreSQL cluster custom Kubernetes resource. PostgreSQL database administration, maintenance, and performance tuning.}

    \item
      \textsc{Mahisoft} (software factory staffing projects from various clients)
      \\ February 2017--July 2017 (Buenos Aires, Argentina): \textbf{Software developer} (client: \textsc{Ten-X})
      \\ August 2016--January 2017 (Caracas, Venezuela): \textbf{Software developer} (client: Performance Settement)
      \\ \small{Full stack Web development using Python with Django and PostgreSQL, containerized development environment and production service administration on Amazon Web Services using Docker Compose with service registration and discovery through Consul and centralized logging with Elasticsearch, Logstash and Kibana, and monitoring using Telegraf, InfluxDB, Grafana and cAdvisor.  Web service development using Spring and MySQL through Spring Boot, JPA, Maven and Docker.}

    \item
      \textsc{Predictvia}
      \\ June 2015--July 2016 (Caracas, Venezuela): \textbf{Software architect}
      \\ \small{Distributed scheduling for computationally intensive machine learning tasks on dynamically provisioned AWS EC2 worker instances based on dataset quality indicators produced by social network data acquisition processes, mostly developed in Python.  Mixed-model, multi-DBMS database architecture, logical design, implementation, operation, performance tuning, and implementation of mechanisms for specific distributed consistency and high availability guarantees for PostgreSQL, RDS Aurora, and MongoDB, with replication and automated failover.  Administration of 10 to 20 AWS EC2 instances with server and service monitoring using Telegraf, InfluxDB, Grafana.}

    \item
      \textsc{Pictune}
      \\ March 2015--September 2015 (Caracas, Venezuela): \textbf{CTO}
      \\ \small{Product design, system architecture, infrastructure administration, database logical design and iOS application development for a social network focused on creative expression through procedural music generation from images.  HTTP API design under the REST architectural style and implementation using the Servant and Yesod Web frameworks for Haskell, PostgreSQL database design and implementation, and iOS 8 mobile application development using Swift, C and Haskell.}

    \item July 2014--February 2015: Continuing studies.

    \item
      \textsc{PRX Control Solutions}
      \\ April 2013--June 2014 (Caracas, Venezuela): \textbf{Software Development Intern}
      \\ \small{Development of a transpiler using Haskell for SQL generation to extend any generic relational database schema with full version control semantics, transparent SQL operation, and an HTTP querying and manipulation API designed under the REST architectural style.  Development of a scalable, dynamic rule system for fraud detection in health insurance claims.  Linux VPS server and Web service administration, monitoring, performance tuning and load balancing using HAproxy, Django, Gunicorn, Yesod, Keter, PHP, Apache and Nginx.}

% Not really important experience, very short, tech I hate, and makes text spill onto a second page.  Meh.
%   \item
%     January 2013--March 2013: \textbf{Programmer}, \textsc{Sucucho}
%     \\ \small{Full stack Web development using PHP with CakePHP and MySQL.}

    \item
      \textsc{Universidad Sim\'on Bol\'{\i}var}
      \\ April 2011--December 2015 (Caracas, Venezuela): \textbf{Undergraduate teaching assistant}
      \\ \small{Teaching undergraduate-level courses on programming language theory, functional programming, compiler construction, Unix system architecture and administration, concurrent programming.}

  \end{itemize}

\end{resume}

\end{document}
